Fast, Scalable Phrase-Based SMT Decoding

### 2016-03-04 acl.2016/acl2016.tex
acl paper

The lexicalized reordering model is trained on parallel data, usually requiring random lookups of the model file during decoding. Using the model can increase translation quality at the cost of longer decoding time. Efforts such as~\newcite{junczys_tsd_2012b} have been made to increase the speed of the model, with some success at low core counts, Figure~\ref{fig:moses-lex-ro}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-lex-ro.png}} 
\end{tabular}
\caption{Comparing Moses decoding time with different Lexicalized Reordering implementations}
\label{fig:moses-lex-ro}
\end{figure}

>>>>

The lexicalized reordering model is trained on parallel data, usually requiring random lookups of the model file during decoding. Using the model can increase translation quality at the cost of longer decoding time. Efforts such as~\newcite{junczys_tsd_2012b} have been made to increase the speed of the model.
